\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References} % Add an entry for this in the table of contents

\bibitem{Gardel}
	Gardel, A., Bravo, I., Jimenez, P., Lazaro, J.L. \& Torquemada, A.\\
	``\textit{Statistical Background Models with Shadow Detection for Video Based Tracking},''\\ Intelligent Signal Processing, 2007. WISP 2007. IEEE International Symposium on?? Page: 1-6.
	
\bibitem{Zivkovic}
	Zivkovic, Z. \& Heijden, F.\\
	``\textit{Efficient Adaptive Density Estimation per Image Pixel for the Task of Background Subtraction},''\\
	Pattern recognition letters, Vol. 27, No. 7. (2006), pp. 773-780.

\vspace{2cm}
\LARGE{\textbf{EXAMPLE REFERENCES ONLY, REMOVE BEFORE HANDING IN}}
\normalsize
\bibitem{CVBook}
	Sonka, M., Hlavac, V. \& Boyle, R. 
	\emph{Image Processing, Analysis, and Machine Vision}.\\
	Toronto: Thompson Learning,
	cop. 2008, 3rd ed.,
	ISBN 0495244384.
	
\bibitem{Wood}
	Wood, J. (2007)
	``\textit{Statistical Background Models with Shadow Detection for Video Based Tracking},''\\
	Master thesis, Linköping University, Department of Electrical Engineering.	

\bibitem{DSPBook}
	Gustafsson, F., Ljung, L. \& Millnert, M.
	\emph{Signal Processing}.\\
	Studentlitteratur, Lund, Sweden,
	2011, 1st ed.,
	ISBN 978--91--44--05835--1.

\bibitem{MOTA}
	Bernardin, K. \& Stiefelhagen, R (2008)\\
	``\textit{Evaluating Multiple Object Tracking Performance: The CLEAR MOT Metrics},''\\
	Interactive Systems Lab, Institut für Theoretische Informatik,\\
	Universität Karlsruhe, 76131 Karlsruhe, Germany

\bibitem{CAVIAR}
	``\textit{CAVIAR: Context Aware Vision using Image-based Active Recognition},''\\
	EC Funded CAVIAR project/IST 2001 37540\\
	http://homepages.inf.ed.ac.uk/rbf/CAVIAR/
	

%\bibitem{somePaper}
%	Q. Lastname,
%	``Some article title,''
%	\emph{Some scientific journal},
%	vol.~1337, no.~1337,
%	pp.~666--1337,
%	month.~1337.

\end{thebibliography}