This section describes what is required by the system in terms of usage and installation. It also covers what is wanted by the user. 

\subsection{Installation}
The installation consists of the placement of one or more cameras, connection of these via Ethernet to a computer, and installation of the software on that computer. The cameras should be placed as described in the user manual with focus on vision rather than precise positioning. The connection via Ethernet is completely provided by the user.     

Once installed the system needs a calibration which is preformed by the user in the calibration program.

The installation and calibration process is described in detail to the user in the user manual.

\subsection{Usage}
When the system is properly installed it can be maneuvered by the user through the interface. The user can now start adding cameras together from the interface. Now the system will start keeping track of the room and continuously provide the user with occupancy statistics about the room. 

\subsection{Maintenance}
The system should be able to run continuously once started, without further maintenance. Additional cameras can not necessarily be added on the fly. 

\subsection{Continued development}
The user interface is initially not prioritized as this is a project mainly in computer vision. This will leave some GUI features open for future development. 

\subsection{Operational requirements}
The user is assumed to have some minor computer skills, but no knowledge whatsoever about computer vision. 


\label{sec:ui_req}
\reqtable
{
	\addreq{The installation proces requires a short manual and no knowledge about advanced computer vision}{1}
	\addreq{Calibration of the system is performed via a calibration program}{1}
	\addreq{The system is self-calibrating}{2}
	\addreq{Software for adding new cameras and/or rooms is provided with the system. \newline
			\textbf{Revised 2013-11-27:} Only single-room - many sensors support is provided.}{1}
	\addreq{Results are presented on the project group webpage}{1}
	\addreq{System is avaliable as an App on AppStore/Android Market}{3}
}