\section{Review of Sprint 0}
\label{sec:sprint0}
\large Period: 2013-09-17 -- 2013-09-30 \\ 
\large Est. time: No estimate was made

\subsection{Sprint backlog}
This sprint is the first one for the project and is thought of as a way of testing the process, which is why no time estimations were made. The main purpose of this sprint was to create frameworks and routines for the continued development.


\itemtable
{
	\additem{Requirement specification: Fix the remaining issues with the requirement specification.}{--}{EF}
	\additem{Project plan: Add the product backlog, due dates and priorities.}{--}{GH, MR}
	\additem{Project plan: Document and process explanation.}{--}{MT, NW}
	\additem{Documentation: Create a template for this document}{--}{MS}
	\additem{Data collection: Gather a first batch of test data using USB cameras.}{--}{MR, AS}
	\additem{Data collection: Find a suitable way of labeling the different video sequences}{--}{EF, MR, AS}
	\additem{Code (general): Create code skeleton, mainloop and interfaces between modules.}{--}{MT, NW}
	\additem{Code (general):Set up a cmake build system for the entire project.}{--}{GH, MS}
	\additem{Code (general): Create a code standard.}{--}{MS, MT}
	\additem{Documentation: Set up DOxygen}{--}{GH, MS}
	\additem{Testing: Set up an outline for some form of automatic testing.}{--}{GH, NW}
	\additem{Technical documentation: Create a template for the final technical documentation.}{--}{AS, MS}
	\additem{Sprint Review Document: Create a template for the Sprint review documents.}{--}{MS}

		
}
\newpage

\subsection{Result}
The result of this sprint can be considered good since all items were completely finished on time. What needs to be improved by in the next sprint is to use the item numbers for the planning meetings on the SCRUM board and when naming issues on git. The reporting of time also has to be improved in order to be able to distribute workload evenly among group members.

\resulttable
{
	\addresult{DONE, but no feedback was recieved from supervisor.}{hours}{EF}
	\addresult{DONE, but no feedback was recieved from supervisor.}{hours}{GH, MR}
	\addresult{DONE, but no feedback was recieved from supervisor.}{hours}{MT, NW}
	\addresult{DONE, resulted in a new backlog item (1).}{hours}{MS}
	\addresult{DONE, but FoV was too narrow using the USB camera.}{hours}{MR, AS}
	\addresult{DONE, CAVIAR GUI is used for labeling.}{hours}{EF, MR, AS}
	\addresult{DONE, resulted in two new backlog items (2 and 3).}{hours}{MT, NW}
	\addresult{DONE.}{hours}{GH}
	\addresult{DONE, see the project wiki page at github.}{hours}{MT, MS}
	\addresult{DONE, see the project wiki page at github.}{hours}{GH, MS}
	\addresult{DONE, however a full system test is not complete as this item was only regarding the framework.}{hours}{GH, NW}
	\addresult{DONE.}{hours}{AS, MS}
	\addresult{DONE.}{hours}{MS}
	
}

\subsection{New Backlog Items}
The first sprint resulted in three backlog items, all of which are listed and described below

\subsubsection{New backlog Item 1}
Adding a template for the receive collection, which is a collection of these documents, one for every sprint that are to be submitted at the end of the course.

\subsubsection{New backlog Item 2}
The algorithm interface in the image processing and the content of the FrameList class.

\subsubsection{New backlog Item 3}
DOxygen comments need to be added to the code skeleton.